### 2009-12-14 trunk/deliverables/D2_2_Ontology/classes.tex
latest ontology changes integrated
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@389 d8b0c59b-6544-0410-94d9-83a5658a058e

\subsubsection{Class: \texttt{fast:Resource}}

@@

\textcolor{white}{\textbf{super\_class\_of}} & \htmlref{\texttt{fast:Screen\_Flow}}{subs:ScreenFlow}, \htmlref{\texttt{fast:Screen}}{subs:Screen}, \htmlref{\texttt{fast:Backend\_Service}}{subs:BackendService}, \htmlref{\texttt{fast:Flow\_Control\_Element}}{subs:FlowControlElement}, \htmlref{\texttt{fast:Operator}}{subs:Operator}, \htmlref{\texttt{fast:Form\_Element}}{subs:FormElement}, \htmlref{\texttt{fast:Condition}}{subs:Condition}, \htmlref{\texttt{fast:WithConditions}}{subs:WithConditions} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fast:contains}}{subs:contains}, \htmlref{\texttt{fast:hasIcon}}{subs:hasIcon}, \htmlref{\texttt{fast:hasScreenshot}}{subs:hasScreenshot} \\ \hline
\textcolor{white}{\textbf{in\_range\_of}} & \htmlref{\texttt{fast:contains}}{subs:contains} \\ \hline

@@

\subsubsection{Class: \texttt{fast:Screen\_Flow}}

@@

\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fast:Resource}}{subs:Resource} \\ \hline

@@

\subsubsection{Class: \texttt{fast:Screen}}

@@

\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fast:Resource}}{subs:Resource} \\ \hline

@@

\subsubsection{Class: \texttt{fast:Backend\_Service}}

@@

\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fast:Resource}}{subs:Resource} \\ \hline

@@

\subsubsection{Class: \texttt{fast:Flow\_Control\_Element}}
\textcolor{white}{\textbf{super\_class\_of}} & \htmlref{\texttt{fast:Screen\_Flow\_Start}}{subs:ScreenFlowStart}, \htmlref{\texttt{fast:Screen\_Flow\_End}}{subs:ScreenFlowEnd}, \htmlref{\texttt{fast:Connector}}{subs:Connector} \\ \hline
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fast:Resource}}{subs:Resource} \\ \hline
\subsubsection{Class: \texttt{fast:Screen\_Flow\_Start}}
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fast:Flow\_Control\_Element}}{subs:FlowControlElement} \\ \hline
\subsubsection{Class: \texttt{fast:Screen\_Flow\_End}}
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fast:Flow\_Control\_Element}}{subs:FlowControlElement} \\ \hline
\subsubsection{Class: \texttt{fast:Connector}}
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fast:Flow\_Control\_Element}}{subs:FlowControlElement} \\ \hline
\subsubsection{Class: \texttt{fast:Operator}}
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fast:Resource}}{subs:Resource} \\ \hline
\subsubsection{Class: \texttt{fast:Form\_Element}}
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fast:Resource}}{subs:Resource} \\ \hline
\subsubsection{Class: \texttt{fast:Condition}}

@@

    the concepts of slot and event. \\ \hline
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fast:Resource}}{subs:Resource} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fast:hasPattern}}{subs:hasPattern}, \htmlref{\texttt{fast:isPositive}}{subs:isPositive} \\ \hline
\textcolor{white}{\textbf{in\_range\_of}} & \htmlref{\texttt{fast:hasPreCondition}}{subs:hasPreCondition}, \htmlref{\texttt{fast:hasPostCondition}}{subs:hasPostCondition} \\ \hline

@@

\subsubsection{Class: \texttt{fast:WithConditions}}

@@

\textcolor{white}{\textbf{description}} & Those kinds of resource which can have pre- or post-conditions 
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fast:Resource}}{subs:Resource} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fast:hasPreCondition}}{subs:hasPreCondition}, \htmlref{\texttt{fast:hasPostCondition}}{subs:hasPostCondition} \\ \hline
\textcolor{white}{\textbf{unionOf}} & \htmlref{\texttt{fast:Screen}}{subs:Screen}, \htmlref{\texttt{fast:Screen\_Flow}}{subs:ScreenFlow} \\ \hline

@@

>>>>

\subsubsection{Class: \texttt{fgo:Resource}}

@@

\textcolor{white}{\textbf{super\_class\_of}} & \htmlref{\texttt{fgo:ScreenFlow}}{subs:ScreenFlow}, \htmlref{\texttt{fgo:Screen}}{subs:Screen}, \htmlref{\texttt{fgo:FlowControlElement}}{subs:FlowControlElement}, \htmlref{\texttt{fgo:ScreenComponent}}{subs:ScreenComponent}, \htmlref{\texttt{fgo:Condition}}{subs:Condition}, \htmlref{\texttt{fgo:Fact}}{subs:Fact}, \htmlref{\texttt{fgo:WithPreConditions}}{subs:WithPreConditions}, \htmlref{\texttt{fgo:WithPostConditions}}{subs:WithPostConditions}, \htmlref{\texttt{fgo:WithConditions}}{subs:WithConditions}, \htmlref{\texttt{fgo:Precondition}}{subs:Precondition}, \htmlref{\texttt{fgo:Postcondition}}{subs:Postcondition}, \htmlref{\texttt{fgo:Pipe}}{subs:Pipe}, \htmlref{\texttt{fgo:Trigger}}{subs:Trigger} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:contains}}{subs:contains}, \htmlref{\texttt{fgo:hasIcon}}{subs:hasIcon}, \htmlref{\texttt{fgo:hasScreenshot}}{subs:hasScreenshot}, \htmlref{\texttt{fgo:hasTag}}{subs:hasTag}, \htmlref{\texttt{fgo:hasVersion}}{subs:hasVersion}, \htmlref{\texttt{fgo:hasId}}{subs:hasId}, \htmlref{\texttt{fgo:hasName}}{subs:hasName}, \htmlref{\texttt{fgo:hasType}}{subs:hasType}, \htmlref{\texttt{fgo:hasDefinition}}{subs:hasDefinition} \\ \hline

@@

\subsubsection{Class: \texttt{fgo:ScreenFlow}}

@@

\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline

@@

\subsubsection{Class: \texttt{fgo:Screen}}

@@

\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasCode}}{subs:hasCode} \\ \hline

@@

\subsubsection{Class: \texttt{fgo:FlowControlElement}}
\textcolor{white}{\textbf{super\_class\_of}} & \htmlref{\texttt{fgo:ScreenFlowStart}}{subs:ScreenFlowStart}, \htmlref{\texttt{fgo:ScreenFlowEnd}}{subs:ScreenFlowEnd}, \htmlref{\texttt{fgo:Connector}}{subs:Connector} \\ \hline
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline
\subsubsection{Class: \texttt{fgo:ScreenFlowStart}}
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:FlowControlElement}}{subs:FlowControlElement} \\ \hline
\subsubsection{Class: \texttt{fgo:ScreenFlowEnd}}
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:FlowControlElement}}{subs:FlowControlElement} \\ \hline
\subsubsection{Class: \texttt{fgo:Connector}}
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:FlowControlElement}}{subs:FlowControlElement} \\ \hline
\subsubsection{Class: \texttt{fgo:ScreenComponent}}
\label{subs:ScreenComponent}
\textcolor{white}{\textbf{label}} & Screen Component \\ \hline
\textcolor{white}{\textbf{description}} & A screen component is any resource which is part of a particular screen. \\ \hline
\textcolor{white}{\textbf{super\_class\_of}} & \htmlref{\texttt{fgo:Operator}}{subs:Operator}, \htmlref{\texttt{fgo:FormElement}}{subs:FormElement}, \htmlref{\texttt{fgo:BackendService}}{subs:BackendService} \\ \hline
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasAction}}{subs:hasAction}, \htmlref{\texttt{fgo:hasTrigger}}{subs:hasTrigger}, \htmlref{\texttt{fgo:hasLibrary}}{subs:hasLibrary} \\ \hline
\subsubsection{Class: \texttt{fgo:Operator}}
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:ScreenComponent}}{subs:ScreenComponent} \\ \hline
\subsubsection{Class: \texttt{fgo:FormElement}}
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:ScreenComponent}}{subs:ScreenComponent} \\ \hline
\subsubsection{Class: \texttt{fgo:BackendService}}

@@

\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:ScreenComponent}}{subs:ScreenComponent} \\ \hline

@@

\subsubsection{Class: \texttt{fgo:Condition}}

@@

    the concepts of slot and event.
	A condition can be seen as a RDF bag of facts, where every fact has to be true
	for the condition be true as well. \\ \hline
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline
\textcolor{white}{\textbf{in\_range\_of}} & \htmlref{\texttt{fgo:hasPreCondition}}{subs:hasPreCondition}, \htmlref{\texttt{fgo:hasPostCondition}}{subs:hasPostCondition}, \htmlref{\texttt{fgo:hasCondition}}{subs:hasCondition} \\ \hline

@@

\subsubsection{Class: \texttt{fgo:Fact}}
\label{subs:Fact}
\textcolor{white}{\textbf{label}} & Fact \\ \hline
\textcolor{white}{\textbf{description}} & A fact is the atomic formal representation of a part of a condition.
	Therefore, several facts compose a condition. \\ \hline
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasPattern}}{subs:hasPattern}, \htmlref{\texttt{fgo:hasPatternString}}{subs:hasPatternString}, \htmlref{\texttt{fgo:isPositive}}{subs:isPositive} \\ \hline
\subsubsection{Class: \texttt{fgo:WithPreConditions}}
\label{subs:WithPreConditions}
\textcolor{white}{\textbf{label}} & With-precondition \\ \hline
\textcolor{white}{\textbf{description}} & Those kinds of resource which can have pre-conditions 
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasPreCondition}}{subs:hasPreCondition} \\ \hline
\textcolor{white}{\textbf{unionOf}} & \htmlref{\texttt{fgo:ScreenFlow}}{subs:ScreenFlow}, \htmlref{\texttt{fgo:Screen}}{subs:Screen}, \htmlref{\texttt{fgo:Action}}{subs:Action} \\ \hline
\subsubsection{Class: \texttt{fgo:WithPostConditions}}
\label{subs:WithPostConditions}
\textcolor{white}{\textbf{label}} & With-precondition \\ \hline
\textcolor{white}{\textbf{description}} & Those kinds of resource which can have pre-conditions 
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasPostCondition}}{subs:hasPostCondition} \\ \hline
\textcolor{white}{\textbf{unionOf}} & \htmlref{\texttt{fgo:ScreenFlow}}{subs:ScreenFlow}, \htmlref{\texttt{fgo:Screen}}{subs:Screen}, \htmlref{\texttt{fgo:ScreenComponent}}{subs:ScreenComponent} \\ \hline
\subsubsection{Class: \texttt{fgo:WithConditions}}

@@

\textcolor{white}{\textbf{description}} & Those kinds of resource which can have both pre- or post-conditions. \\ \hline
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline
\textcolor{white}{\textbf{unionOf}} & \htmlref{\texttt{fgo:WithPreConditions}}{subs:WithPreConditions}, \htmlref{\texttt{fgo:WithPostConditions}}{subs:WithPostConditions} \\ \hline

@@

\subsubsection{Class: \texttt{fgo:Action}}
\label{subs:Action}
\textcolor{white}{\textbf{label}} & Action \\ \hline
\textcolor{white}{\textbf{description}} & An action represents a specific routine which will be performed when a certain
	condition is fulfilled within a certain screen component (i.e., the action `showTable' will
	be performed when data from a service is received). \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasUse}}{subs:hasUse} \\ \hline
\textcolor{white}{\textbf{in\_range\_of}} & \htmlref{\texttt{fgo:hasAction}}{subs:hasAction} \\ \hline
\subsubsection{Class: \texttt{fgo:Library}}
\label{subs:Library}
\textcolor{white}{\textbf{label}} & Action \\ \hline
\textcolor{white}{\textbf{description}} & An action represents a specific routine which will be performed when a certain
	condition is fulfilled within a certain screen component (i.e., the action `showTable' will
	be performed when data from a service is received). \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasLanguage}}{subs:hasLanguage}, \htmlref{\texttt{fgo:hasSource}}{subs:hasSource} \\ \hline
\textcolor{white}{\textbf{in\_range\_of}} & \htmlref{\texttt{fgo:hasLibrary}}{subs:hasLibrary} \\ \hline
\subsubsection{Class: \texttt{fgo:Precondition}}
\label{subs:Precondition}
\textcolor{white}{\textbf{label}} & Precondition \\ \hline
\textcolor{white}{\textbf{description}} & A precondition is a satisfied condition within a screenflow. It can be seen
    as an input of the screenflow. \\ \hline
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasCondition}}{subs:hasCondition} \\ \hline
\subsubsection{Class: \texttt{fgo:Postcondition}}
\label{subs:Postcondition}
\textcolor{white}{\textbf{label}} & Postcondition \\ \hline
\textcolor{white}{\textbf{description}} & A postcondition is a result condition within a screenflow. It can be seen
    as an output of the screenflow. \\ \hline
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasCondition}}{subs:hasCondition} \\ \hline
\subsubsection{Class: \texttt{fgo:Definition}}
\label{subs:Definition}
\textcolor{white}{\textbf{label}} & Resource definition \\ \hline
\textcolor{white}{\textbf{description}} & Structural and behaviour definition of a resource. \\ \hline
\textcolor{white}{\textbf{super\_class\_of}} & \htmlref{\texttt{fgo:ScreenDefinition}}{subs:ScreenDefinition} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:contains}}{subs:contains} \\ \hline
\textcolor{white}{\textbf{in\_range\_of}} & \htmlref{\texttt{fgo:hasDefinition}}{subs:hasDefinition} \\ \hline
\subsubsection{Class: \texttt{fgo:ResourceReference}}
\label{subs:ResourceReference}
\textcolor{white}{\textbf{label}} & Resource reference \\ \hline
\textcolor{white}{\textbf{description}} & It`s a reference to a certain resource. Needs a 'id' for internal
	identification for the resource which is referencing it, and the `uri' of the
	resource. \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasId}}{subs:hasId}, \htmlref{\texttt{fgo:hasUri}}{subs:hasUri} \\ \hline
\textcolor{white}{\textbf{in\_range\_of}} & \htmlref{\texttt{fgo:contains}}{subs:contains}, \htmlref{\texttt{fgo:hasUse}}{subs:hasUse} \\ \hline
\subsubsection{Class: \texttt{fgo:ScreenDefinition}}
\label{subs:ScreenDefinition}
\textcolor{white}{\textbf{label}} & Screen definition \\ \hline
\textcolor{white}{\textbf{description}} & Behaviour definition of a screen. This will contain which form, operators and 
	backend services the screen is composed, and how they are connected. \\ \hline
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:Definition}}{subs:Definition} \\ \hline
\subsubsection{Class: \texttt{fgo:Pipe}}
\label{subs:Pipe}
\textcolor{white}{\textbf{label}} & pipe or connector \\ \hline
\textcolor{white}{\textbf{description}} & Define a pipe or connector between two resources. The connection is made
	specifying the conditions which will be connected. \\ \hline
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasIdBBFrom}}{subs:hasIdBBFrom}, \htmlref{\texttt{fgo:hasIdConditionFrom}}{subs:hasIdConditionFrom}, \htmlref{\texttt{fgo:hasIdBBTo}}{subs:hasIdBBTo}, \htmlref{\texttt{fgo:hasIdConditionTo}}{subs:hasIdConditionTo}, \htmlref{\texttt{fgo:hasIdActionTo}}{subs:hasIdActionTo} \\ \hline
\subsubsection{Class: \texttt{fgo:Trigger}}
\label{subs:Trigger}
\textcolor{white}{\textbf{label}} & Trigger \\ \hline
\textcolor{white}{\textbf{description}} & Define a... \\ \hline
\textcolor{white}{\textbf{sub\_class\_of}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline
\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasIdBBFrom}}{subs:hasIdBBFrom}, \htmlref{\texttt{fgo:hasIdBBTo}}{subs:hasIdBBTo}, \htmlref{\texttt{fgo:hasIdActionTo}}{subs:hasIdActionTo}, \htmlref{\texttt{fgo:hasNameFrom}}{subs:hasNameFrom} \\ \hline
\subsubsection{Class: \texttt{fgo:FormDefinition}}
\label{subs:FormDefinition}
\textcolor{white}{\textbf{label}} & Form Definition \\ \hline
\subsubsection{Class: \texttt{fgo:OperatorDefinition}}
\label{subs:OperatorDefinition}
\textcolor{white}{\textbf{label}} & Operator Definition \\ \hline
\subsubsection{Class: \texttt{fgo:BackendServiceDefinition}}
\label{subs:BackendServiceDefinition}
\textcolor{white}{\textbf{label}} & Backend Service Definition \\ \hline
